\thesistitle

### 2019-07-24 sections/background.tex
Fix references

\section{Clone Types} \label{chap:backgroundclonetypes}
\simon{What is Structurally/syntactically/functionally/textually, ect ect, all words before EQUAL}
Duplication in code is found in many different forms. Most often duplicated code is the result of a programmer reusing previously written code \cite{haefliger2008code, baxter1998clone}. Sometimes this code is then adapted to fit the new context. To reason about these modifications, several clone types have been proposed. These clone types are described in Roy et al \cite{roy2007survey}:
\begin{displayquote}
\textbf{Type I:} Identical code fragments except for variations in whitespace (may be also variations in layout) and comments.\\
\textbf{Type II:} Structurally/syntactically identical fragments except for variations in identifiers, literals, types, layout and comments.\\
\textbf{Type III:} Copied fragments with further modifications. Statements can be changed, added or removed in addition to variations in identifiers, literals, types, layout and comments.\\
\textbf{Type IV:} Two or more code fragments that perform the same computation but implemented through different syntactic variants.
\end{displayquote}
A higher type of clone means that it's harder to detect and refactor. There are many studies that adopt these clone types, analyzing them further and writing detection techniques for them \cite{sajnani2016sourcerercc, kodhai2010detection, van2019novel}.

@@

\section{Refactoring methods}
One of the main drivers for starting this research is the recent release of the second edition of Martin Fowlers' Refactoring book \ref{fowler2018refactoring}. This book has been updated to the modern state of software engineering. The sentence in which he stresses the importance of unifying duplication in source code remains present in both books \ref{fowler1999refactoring, fowler2018refactoring}.

@@

\subsection{Extract Method}
Method extraction is one of the most used methods of refactoring duplication in source code. Several studies have already concluded that most duplication in source code is found in the body of methods \ref{lozano2007evaluating, white2016deep, bergman2004ethnographic}. Method extraction can move matching functionality between methods to a common place: a new method. An example of this procedure is displayed in figure \ref{fig:extractmethod}.

@@

\subsection{Move method}
In the example of the previous section, both duplicated parts are in the same method. However, a study by Fontana et al. \ref{fontana2015duplicated} shows that this is most often not the case. Based on the relation between clone instances, the extracted method must be moved to be accessible by all locations of the clone instances. This might require different techniques.

\subsubsection{Pull up method}
A refactoring technique to move a method up in its inheritance structure is called ``Pull up method'' \ref{fowler2018refactoring}. This way, if cloned methods are related in any way through inheritance, they can be called by both classes by placing the method in a class they both have in common. This way its possible to refactor both fully cloned methods (by just pulling up the method) and partially cloned methods (by first performing method extraction and then pulling up the refactored method).

@@

\subsubsection{Providing default implementations for common functionality}
Looking specifically at the Java programming language, recent versions of Java introduce a new method of reducing duplication through refactoring. Java has the concept of \textit{interfaces} as an abstract type that is used to specify a behavior that classes must implement. Since Java version 8, Java also supports default implementations to be provided in interfaces \ref{mohnen2002interfaces}. This gives an opportunity to make the relation between classes explicit and reduce duplication. It can be used in instances where creating a new parent class for duplicated classes is undesirable.

>>>>

\section{Clone Types} \label{chap:backgroundclonetypes}
Duplication in code is found in many different forms. Most often duplicated code is the result of a programmer reusing previously written code \cite{haefliger2008code, baxter1998clone}. Sometimes this code is then adapted to fit the new context. To reason about these modifications, several clone types have been proposed. These clone types are described in Roy et al \cite{roy2007survey}:
\begin{displayquote}
\textbf{Type I:} Identical code fragments except for variations in whitespace (may be also variations in layout) and comments.\\
\textbf{Type II:} Structurally/syntactically identical fragments except for variations in identifiers, literals, types, layout and comments.\\
\textbf{Type III:} Copied fragments with further modifications. Statements can be changed, added or removed in addition to variations in identifiers, literals, types, layout and comments.\\
\textbf{Type IV:} Two or more code fragments that perform the same computation but implemented through different syntactic variants.
\end{displayquote}
A higher type of clone means that it's harder to detect and refactor. There are many studies that adopt these clone types, analyzing them further and writing detection techniques for them \cite{sajnani2016sourcerercc, kodhai2010detection, van2019novel}.

@@

\section{Refactoring methods}
Martin Fowler recently released the second edition of his Refactoring book \cite{fowler2018refactoring}. This book has been updated to the modern state of software engineering. The sentence in which he stresses the importance of unifying duplication in source code remains present in both books \cite{fowler1999refactoring, fowler2018refactoring}.

@@

\subsection{Extract Method}
Method extraction is one of the most used methods of refactoring duplication in source code. Several studies have already concluded that most duplication in source code is found in the body of methods \cite{lozano2007evaluating, white2016deep, bergman2004ethnographic}. Method extraction can move matching functionality between methods to a common place: a new method. An example of this procedure is displayed in figure \cite{fig:extractmethod}.

@@

\subsection{Move method}
In the example of the previous section, both duplicated parts are in the same method. However, a study by Fontana et al. \cite{fontana2015duplicated} shows that this is most often not the case. Based on the relation between clone instances, the extracted method must be moved to be accessible by all locations of the clone instances. This might require different techniques.

\subsubsection{Pull up method}
A refactoring technique to move a method up in its inheritance structure is called ``Pull up method'' \cite{fowler2018refactoring}. This way, if cloned methods are related in any way through inheritance, they can be called by both classes by placing the method in a class they both have in common. This way its possible to refactor both fully cloned methods (by just pulling up the method) and partially cloned methods (by first performing method extraction and then pulling up the refactored method).

@@

\subsubsection{Providing default implementations for common functionality}
Looking specifically at the Java programming language, recent versions of Java introduce a new method of reducing duplication through refactoring. Java has the concept of \textit{interfaces} as an abstract type that is used to specify a behavior that classes must implement. Since Java version 8, Java also supports default implementations to be provided in interfaces \cite{mohnen2002interfaces}. This gives an opportunity to make the relation between classes explicit and reduce duplication. It can be used in instances where creating a new parent class for duplicated classes is undesirable.
